Thomas et al. 2025

### 2025-02-24 IndividualStudies/AT_2025.qmd
Trying to adjust formatting of Dot Plots

```{r, echo=FALSE, include=FALSE}

@@

AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")

# Organize the hit annotations as factors
AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(AT_2025_Long)/2)){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked_PE <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

# Applies the ID column to the PA results
AT_2025_ranked_PA <- AT_2025_Long |>
    arrange(logFC) |>
	filter(LipidProbe == "PA") |>
	mutate(ID = ID)

@@

VolcanoPlotStandardized(AT_2025_Long)

@@

## Enriched proteins

@@

## Creates a reactive dataframe
AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_Long_reactive,
                  group = ~hit_annotation)
)

@@

## Displays the reactive dataframe
datatable(AT_2025_Long_reactive, options = list(pageLength = 20))

>>>>

@@

AT_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))

# Organize the hit annotations as factors
AT_2025$hit_annotation <- factor(pull(AT_2025, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

# Building an ID column to maintain the order on the x-axis
ID <- c()
for(i in 0:(nrow(AT_2025)/2)){
	ID[i] = i
}

# Applies the ID column to the PE results
AT_2025_ranked_PE <- AT_2025 |>
    arrange(logFC) |>
	filter(LipidProbe == "PE") |>
	mutate(ID = ID)

# Applies the ID column to the PA results
AT_2025_ranked_PA <- AT_2025 |>
    arrange(logFC) |>
	filter(LipidProbe == "PA") |>
	mutate(ID = ID)

@@

VolcanoPlotStandardized(AT_2025)

@@

## Gene Ontology enrichment

**In beta: GO analysis still under development**

#### Cell Compartment

:::{.border}

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)

#### Molecular Function

:::{.border}

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)

#### Biological Process

:::{.border}

<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)

## Data exploration and download

@@

## Creates a reactive dataframe
AT_2025_reactive <- crosstalk::SharedData$new(AT_2025)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = AT_2025_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = AT_2025_reactive,
                  group = ~hit_annotation)
)

@@

## Displays the reactive dataframe
datatable(AT_2025_reactive, options = list(pageLength = 20))
